Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-18 articles/cycle/alps-cycle.tex
Add references on timing.

    The timing of the LGM has been documented by radiocarbon and cosmogenic
    isotope dating techniques at multiple glacier lobes around the Alps.
    These data indicate that Alpine glaciers reached their maximum extent
    about synchronously with the Laurentide ice sheet around 25\,ka, but
    glacier lobes stayed in the foreland until as late as 20\,ka, a time
    around which the Fennoscandian ice sheet reached is maximum, while the
    Laurentide ice sheet was already in decay.

    In our simulation, the maximum areal cover is reached at 24.57\,ka
    (Fig.~\ref{fig:lgmvel}a), yet individual glacier lobes reach their
    maximum extent at different ages (Fig.~\ref{fig:timing}). For instance, the
    Dora Riparia, Ivrea, and Tagliamento glaciers reach an early maximum before
    27\,ka, the Durance, Rhone, Inn, Enns, Ticino, and Garda glaciers reach
    their maximum thickness in phase with the global Alpine areal maximum
    around 25\,ka, while the Isère, Como and Iseo glaciers reach a late maximum
    after 24\,ka (Fig.~\ref{fig:timing}). Remarkably, peripheral ice caps on
    the Vercors, Jura Mountains, Black Forest and Hochschwab reach their
    maximum extent even later, locally after 21\,ka.

@@

    \todo{look for references, add location names on Fig.~\ref{fig:lgmvel}.}

>>>>

    The timing of the LGM has been documented by radiocarbon and cosmogenic
    isotope dating techniques at multiple locations around the Alps (cf.
    \citealp[Fig.~5]{Wirsig.etal.2016} for a review and the more recent
    publications by \citealp{Monegato.etal.2017, Federici.etal.2017}). These
    data indicate that Alpine glaciers reached their maximum extent between 20
    and 26\,ka (calibrated \chem{^{14}C} or \chem{^{10}Be} ages), but glacier
    lobes stayed in the foreland until as late as 22 to 17\,ka, when they
    experienced rapid retreat synchronously to lowering of the ice surface in
    the mountains (\citealp[Fig.~5]{Wirsig.etal.2016},
    \citealp[Fig.~3]{Monegato.etal.2017}).

    \note{Please edit or complete with more references if needed}

    In our simulation, the maximum areal cover is reached at 24.57\,ka
    (Fig.~\ref{fig:lgmvel}a), yet individual glacier lobes reach their
    maximum extent at different ages (Fig.~\ref{fig:timing}). For instance, the
    Dora Riparia, Ivrea, and Tagliamento glaciers reach an early maximum before
    27\,ka, the Durance, Rhone, Inn, Enns, Ticino, and Garda glaciers reach
    their maximum thickness in phase with the global Alpine areal maximum
    around 25\,ka, while the Isère, Como and Iseo glaciers reach a late maximum
    after 24\,ka (Fig.~\ref{fig:timing}). Remarkably, peripheral ice caps on
    the Vercors, Jura Mountains, Black Forest and Hochschwab reach their
    maximum extent even later, locally after 21\,ka (Fig.~\ref{fig:timing}).

@@
